\textbf{CSDS 440 Class Project: \\Adversarial Machine Learning}

### 2020-12-05 report/article.tex
📦 Add deliverable final report.

\subsection{Minyang Tie's Individual Report}

\subsection{Alex Useloff's Individual Report}

\subsection{Austin Keppers' Individual Report}
\subfile{individual_reports/agk51}

\subsection{David Meshnick's Individual Report}
\subfile{individual_reports/dcm101}

\section{Comparative Study and Discussion}

@@

Likewise, we opted to not compare any other algorithm except \ilc{Backdoor} to against \ilc{Neural Cleanse}, as: Minyang please input here.

@@

We believe this have something to do with the fact \ilc{SS} look into the activations of neuros of adversarial pattern and either force-zero or oppress them. As \ilc{HSJ} being on the decisions boundaries (implied by the low \textit{pertubation budget}), a \ilc{HSJ}-generated adversarial imag might be considered to have adversarial patterns of many kinds and therefore being detected by the defense algorithm.

Minyang, please correct me if I am wrong and add some insight.

@@

Minyang please explain why this works.

@@

In a partical sense, it might be best

>>>>

\newpage
\subsection{Minyang Tie's Individual Report}

\newpage
\subsection{Alex Useloff's Individual Report}

\newpage
\subsection{Austin Keppers' Individual Report}

\newpage
\subsection{David Meshnick's Individual Report}

\newpage
\section{Comparative Study and Discussion}

@@

Likewise, we opted to not compare any other algorithm except \ilc{Backdoor} to against \ilc{Neural Cleanse}, as unlearning the backdoor by retraining is one of the Neural Cleanse method, the defense of unlearning retraining is depend on the pattern. Since the Backdoor algorithm is a pattern attack algorithm, so the comparison between Backdoor and unlearning retraining is the most reasonable part. Also, retraining is a is a commonly used defense method, here we just specifically retrain the pattern of backdoor insert.

@@

We believe this have something to do with the fact \ilc{SS} set the value of each pixel to be the mean value of the pixels around this pixel and it can make the pixel value become more continuous. As \ilc{HSJ} being on the decisions boundaries (implied by the low \textit{pertubation budget}),
Thus the mean value set by \ilc{SS} can used to vague the boundaries to defense.

@@

\ilc{Neural Cleanse} is our implemented defense algorithm focus on Unlearning the backdoor by retraining，the algorithm is defend by train infected DNN to recognize correct labels. Here we specifically retrain the pattern of \ilc{Backdoor} insert as mentioned on Section $3.1.4$. Thus Against the \ilc{Backdoor} attack, \ilc{Neural Cleanse} can achieve a very good defense effect.\newline
By the graph, the Defensive Accuracy is $70.89\%$ (Note we train the whole \textit{MINIST} dataset), which is a very good defence accuracy. In this case, we do not want to compare with other attack algorithm, because the essence of Unlearning retraining is to allow the neural network to resist the influence of external patterns, so retraining is to use pattern to modify the data of the test set and then for training，therefore only \ilc{Backdoor} we implemented is pattern attack, that is why we only compare \ilc{Backdoor} to against \ilc{Neural Cleanse} on this section.

@@
